Regression Cube Analysis of Cohort Study Data

### 2015-03-29 draft.tex
minor revisions

Our contributions are:
\begin{itemize}
	\item An overview visualization technique representing feature interactions using target features.
	\item Visualization techniques, which incorporate overview visualizations of all regression analyses at once as well as details on demand techniques for in-depth investigations of feature relationships.
	\item Freely adjustable regression formulas provide a simple, yet powerful way to adjust the regression analysis to specific hypotheses about the data.
	\item The analysis of confounding variables by providing comparison views between different formula results.
%	\item The open and web-based approach of the system allows for analysis of any data using the presented method.
	\item The expansion and adaption of our method to any data with our open web-based system.
\end{itemize}
%%
The term `Regression Cube' has been used for the detailed analysis of one or a small number of regression models \cite{Chan, Ahmadi}.
%%
They extend 2D scatter plots to display detailed information about a regression model.
%%
In behalf of that, we declare our visualization technique for comparing and analyzing a large number of different regression models with different input features as Regression Cube.
%%
\section{Epidemiological Background} \label{sec:Background}
%%
This section covers the epidemiological workflow and requirements.
%%
\subsection{Epidemiological Workflow} \label{EpidemiologicalWorkflow}
Epidemiological research is performed by experts from different academic disciplines, such as physicians, statisticians and medical computer scientists focusing on biometrics and image segmentation.
%%
Their goal is to derive disease-specific risk factors by assessing epidemiological features using statistical methods.
%%
As described by Thew et al. \cite{Thew2009} the epidemiological workflow is divided into these different steps:
\begin{itemize}
	\item Clinicians make observations in the daily practice, which are translated into hypotheses.
	\item Epidemiologists compile a list of variables depicting the hypothesis and include confounding variables.
	\item Statisticians assess the association of the derived features towards the investigated disease.
\end{itemize}
%%
Relative risks can be determined if a statistical resilient association of features towards a condition is extracted.
%%
They indicate the per-subject chance of developing the disease.
%%
Reproducibility of results is an epidemiological key requirement and guides all analyses steps.
%%
Statistical programs, such as \texttt{SPSS}, are used to analyze the data using the classical sequential epidemiological workflow. Hence, images are mostly used for the communication of results, rather than for providing insight into the data.
%%

In \cite{Klemm2014VIS} we described an Interactive Visual Analysis approach for image-centric cohort study data, which connects to the variable listing step.
%%
The methods aim to derive hypotheses through analysis of the data and observations about previously unknown feature correlations.
%%
Employing \emph{hypotheses generation} requires overview visualizations of feature correlations, which are not supported by standard statistical processors.
%%
In this work, we focus on a similar approach to deriving insight and even new hypotheses through the data rather than using it just for confirmatory analysis.
%An alternative data-driven approach is described as follows.
%%
% \paragraph{Data Driven Hypothesis-Generation-based Analysis.}
% We already described an Interactive Visual Analysis approach for image-centric cohort study data, which connects to the variable listing step \cite{Klemm2014VIS}.
% %%
% The methods aim to derive hypotheses through analysis of the data and observations about previously unknown feature correlations.
% %%
% Employing \emph{hypotheses generation} requires overview visualizations of feature correlations, which are not supported by standard statistical processors.

\subsection{Epidemiological Data} \label{sec:EpidemiologicalData}
%%
%\com{Bernhard: Due to overlaps to VIS'14 paper in this section, this can be shortened. E.g. "More discussion of data types and characteristics can be found in [...]"}
%%
There are many data acquisition modalities available to epidemiologists, which are suitable for different analysis types.
%%
%We focus on cohort studies are a major epidemiological tool for gathering epidemiological features.
We focus on cohort studies, which impose the largest data sets and yield a highly heterogenous and incomplete information space.
%%
Subject data are collected either towards a specific disease or with the widest range possible.
%%
The latter allows the data set to be assessed towards different diseases.
%%
The feature space comprises information about lifestyle, somatometric variables, medical parameters, genetic data as well as medical image data.
%%
These features are derived through different modalities, such as questionnaires, medical examinations or laboratory analyses.
%%
Many features are sparse, such as follow up questions about a medication or treatment of a certain disease.
%%
Other features are exclusive for a sub-group, such as women-specific questions, e.g., number of born children or period status.
%%
%\com{Restriction of amount of data because it must not be triangulated and because the ethics committees are very restrictive}

%\paragraph{Data Types.}
%%
Medical status variables or lifestyle factors are often of \emph{dichotomous} (binary) type.
%%
The data space comprises continuous variables (somatometric variables, such as body weight) as well as categorical variables (e.g. graduation type).
%%
The data heterogeneity has to be taken into account when the analysis method is chosen.
%%
Continuous data are often discretized (e.g. 10 year steps for age) to equalize the variable types and to simplify the method selection.
%%
However, this should be avoided, since it reduces the information space and also introduces a new information bias, as assumptions are modeled through the discretization.
%%

Medical image data is also acquired and analyzed in modern cohort studies.
%%
We incorporate image-derived features, but do not put focus on analyzing image data.
%%
More discussion of cohort study data types and characteristics can be found in \cite{Klemm2014VIS, Toennies2015, Preim2014}.
%%
%\paragraph{Image Data.}
% \com{Can probably be cut (reference to Klaus' Paper for more details on this) (see Bernhards comment above)}
% %%
% Since the Rotterdam study, many modern cohort studies include medical image data.
% %%
% For ethical reasons, the imaging modalities usually not include ionizing radiation.
% %%
% The image quality is often inferior to clinical standards, which is a tradeoff between time and cost \cite{Preim2014}.
% %%
% These data are hard to analyze as they require segmentations to outline structures of interest.
% %%
% This process is prone to inter- and intra-observer variability when carried out manually.
% %%
% Automatic or semi-automatic solutions are a remedy for this problem, but are costly and need to be tailored to the structure of interest \cite{Toennies2015}.
% %%
% Image-derived variables are either dichotomous variables indicating a medical finding by a radiologist or continuous, describing the shape of segmented structures (e.g. volume or diameter).
\\\\
%\paragraph{Confounding Features.}
Features influencing the exposure as well as the outcome of an analysis are called \emph{confounders} and have to be specially treated.
%Confounding features have to be considered in epidemiological analysis, as they influence both the exposure as well as the outcome of an analysis.
%%
%Features influencing the exposure as well as the outcome of an analysis are called confounders.
%%
The analysis model has to be adjusted by normalizing all included features towards the confounder.
%%
\emph{Age} is included as confounder in almost any epidemiological analysis, since most diseases (such as different cancer types) are more likely with increasing age.
%%
It also influences the general body condition and thereby almost all features acquired through cohort studies.
%%
Another important confounder is \emph{Gender}.
%%
Other confounders have to be selected by epidemiologists specific to the investigated condition.

@@

\paragraph{Regression Analysis Notation.} Regression formulas are usually denoted as follows:
%%
\begin{equation}
Dependent \sim Independent_1 + ... + Independent_n
%Dependent \sim \sum_{i=1}^n Independent_i
\label{eq:RegressionNotation}
\end{equation}
%%
A example of a regression formula would be $Kidney\_Disorder ~ Smoking + Obesity$.
The most used regression operators comprise:
%%
\begin{itemize}
	\item $+,-$ inclusion/exclusion of the variable,
	\item $:$ inclusion of interactions between the variables (e.g. $x:y$),
	\item $*$ inclusion the variables as well as their interactions (e.g. $x*y$)
	\item $|$ (conditioning) inclusion of variable x, given y (e.g. $x|y$)
\end{itemize}
%%
The type of the target feature restricts the regression type.
%%
Different regression types are available, we focus on the following:
%%
\paragraph{Linear Regression for Continuous Target.} The basic type is the linear regression, creating a linear map from the space comprising the \emph{independent} features to the \emph{dependent} features.
%%
The \emph{dependent} variable has to be of a continuous type.
%%

\paragraph{Logistic Regression for Dichotomous Target.} Logistic regression implies a dichotomous target variable.
%%
The target is described by fitting a logistic function.
%%
Logistic models as opposed to linear models do not allow for extracting an $R^2$ quality of fit value.
%%
Therefore, pseudo-$R^2$ values are extracted, such as the \emph{Nagelkerke $R^2$}, which mimics the behavior of the $R^2$.
%%
\emph{Nagelkerke $R^2$} cannot be compared to $R^2$ values extracted from linear regression model.

@@

\subsection{The Study of Health in Pomerania (SHIP)}
The \texttt{SHIP}, located in Northern Germany, aims to characterize health and disease in the widest range possible \cite{Volzke2011}.
%%
It does not focus on a specific disease, making the data set open for many diseases.
%%
Unique for the \texttt{SHIP} is the acquisition of medical image data per cohort subject.
%%
A second cohort, \texttt{SHIP-TREND} was started in 2012.
%%
Data for both cohorts are examined in a 5-year time span.
%%
New parameters are added in each iteration, extending the range of investigated diseases.
%%
For the latest two acquisitions (\texttt{SHIP-2} and \texttt{SHIP-TREND-0}), MRI scans are included into the cohort \cite{Hegenscheid2009, Ivanovska2014}.
%%
However, most examinations occur in all stages and are performed according to the same instructions to enable comparisons over the different stages of the study ("\emph{method loyality}").
%%
%Starting in 1997 with a cohort of 4,308 subjects, the \texttt{SHIP}, located in Northern Germany, aims to characterize health and disease in the widest range possible \cite{Volzke2011}.
%After the pioneering Rotterdam study (started in 1990), several MR imaging study initiatives were initiated.
%
%They slightly differ in clinical focus, acquired data and epidemiological research questions.
%
%Starting in 1997 with a cohort of 4,308 subjects, the \texttt{SHIP}, located in Northern Germany, aims to characterize health and disease in the widest range possible \cite{Volzke2011}.
%
%Data are collected without focus on a group of diseases.
%
%This allows to query the data regarding many diseases and conditions.
%
%
\section{Prior and Related Work}
%% https://en.wikipedia.org/wiki/Exploratory_data_analysis#cite_note-Tukey1977-4
In 1977, Tukey already stated that data is too often only analyzed using confirmatory data analysis \cite{Tukey}.
%%
He emphasized the need to use data to derive hypotheses instead, which can then be tested again.
%%
In this section we present prior and related work trying to achieve this goal.
%%
%We put each paper in relation to our work, derive ideas and point out differences, starting with the works closest to ours:
%%
\\\\
The work of Piringer et al. \cite{Piringer}, Chan et al. \cite{Chan}, Angelelli et al. \cite{Angelelli} and Zhang et al. \cite{Zhang2014} are closest related to ours regarding different aspects.
%% HyperMoVal: Interactive Visual Validation of Regression Models for Real-Time Simulation
Akin to our approach, Piringer et al. \cite{Piringer} propose methods for visualizing regression analysis results and properties for developing car engines.
%%
Their main goal is to assess the pairwise influence of independent features towards the target feature using a plot matrix displaying models as contours.
%%
They also incorporate 3D visualizations for each pairwise combination, but mainly because its popularity with their target domain engineers.
%%
Linked views of model deviations allow to select outliers.
%%
This limits the method to comparing a few models at once as the plot matrix gets complex with increasing feature number.
%%
The main difference is their focus on analyzing one complex model in detail, yielding extensive plots, while we analyze a large amount of simpler models towards \emph{different} features.
%%
They also focus on metric features, while we process categorical data as well.
%%
%We share the matrix-arrangement of results depicting relationships between independent features in a model.

@@

%% TODO: Check DLPD for correct page numbers
While the presented techniques were well received by the epidemiological experts, the explanatory power towards back pain was limited, yielding an analysis based on image-derived features, such as extracting and analyzing curvature, torsion and angle of the lumbar spine \cite{Klemm2015}.
%%
%These measures were analyzed using a novel decision tree quality plot towards non-image data.
%%
We concluded that the model quality is insufficient to characterize back pain.
\\\\
The difference of the presented approach towards our previous and related work is twofold:
\begin{enumerate}
	\item We focus on large scale analysis of a vast number of linear and logistic regression-models by assessing their quality-of-fit using descriptive metrics.
	\item The analysis is conducted towards a target feature and incorporates expert knowledge via the regression model definition rather than subdividing the underlying data.
\end{enumerate}
%%
\section{Regression Cube Analysis of Cohort Study Data}
% TODO: Do we need a preprocessing section?
%\com{Add Data Preprocessing Section.}
%%
The basic idea of our \emph{Regression Cube} is to provide an overview visualization of large cohort study data sets towards target variables.
%%
Overview visualizations of feature relationships as presented by Angelelli et al. \cite{Angelelli} are often focused on relationships between the visualized features.
%%
Correlation metrics, such as the \emph{Pearson product-moment correlation coefficient} or \emph{Cram\'{e}r's V} contingency values are incorporated to achieve this goal.
%%
In epidemiology, these relationships are also of interest, but rather w.r.t. their explanatory power towards the target feature.
%%
These target features often indicate the presence of the investigated disease.
%%
As described in Section \ref{sec:RegressionAnalysis}, regression analysis is the statistical tool of choice for analyzing these relationships.
%%
% unified -> singular [Steffi?]
A regression model is based on expert knowledge, there is no singular rule how to apply them to a given set of features. Thus, they have to be applied with care.
%%
\subsection{Cube Description Using Regression Formula Notation}
%%
Expert knowledge is integrated into regression analysis by the regression formulas.
%%
As described in Section~\ref{sec:RegressionAnalysis}, the formula input influences the type of the chosen regression method as well as the \emph{independent} features describing the target.
%%
%In order to calculate all combinations of two to three independent features, we can apply  \emph{Regression Cube} aims to 
%%

@@

The major advantage of this notation is that it comes natural to anyone familiar with regression analysis since it is the standard way of expression 

>>>>

Our contributions are:
\begin{itemize}
	\item An overview visualization technique representing feature interactions using target features.
	\item Visualization techniques, which incorporate overview visualizations of all regression analyses at once as well as details on demand techniques for in-depth investigations of feature relationships.
	\item Freely adjustable regression formulas provide a simple, yet powerful way to adjust the regression analysis to specific hypotheses about the data.
	\item The analysis of confounding variables by providing comparison views between different formula results.
%	\item The open and web-based approach of the system allows for analysis of any data using the presented method.
	\item The expansion and adaption of our method to any data with our open web-based system.
\end{itemize}
%%
The term `Regression Cube' has been used for the detailed analysis of one or a small number of regression models \cite{Chan, Ahmadi}.
%%
They extend 2D scatter plots to display detailed information about a regression model.
%%
In behalf of that, we declare our visualization technique for comparing and analyzing a large number of different regression models with different input features as Regression Cube.
%%
\section{Epidemiological Background} \label{sec:Background}
%%
This section covers the epidemiological workflow and requirements.
%%
\subsection{Epidemiological Workflow} \label{EpidemiologicalWorkflow}
Epidemiological research is performed by experts from different academic disciplines, such as physicians, statisticians and medical computer scientists focusing on biometrics and image segmentation.
%%
Their goal is to derive disease-specific risk factors by assessing epidemiological features using statistical methods.
%%
As described by Thew et al. \cite{Thew2009} the epidemiological workflow is divided into these different steps:
\begin{itemize}
	\item Clinicians make observations in the daily practice, which are translated into hypotheses.
	\item Epidemiologists compile a list of variables depicting the hypothesis and include confounding variables.
	\item Statisticians assess the association of the derived features towards the investigated disease.
\end{itemize}
%%
Relative risks can be determined if a statistical resilient association of features towards a condition is extracted.
%%
They indicate the per-subject chance of developing the disease.
%%
Reproducibility of results is an epidemiological key requirement and guides all analyses steps.
%%
Statistical programs, such as \texttt{SPSS}, are used to analyze the data regarding the classical sequential epidemiological workflow. Hence, images are mostly used for the communication of results, rather than for providing insight into the data.
%%

In \cite{Klemm2014VIS} we described an Interactive Visual Analysis approach for image-centric cohort study data, which connects to the variable listing step.
%%
The methods aim to derive hypotheses through analysis of the data and observations about previously unknown feature correlations.
%%
Employing \emph{hypothesis generation} requires overview visualizations of feature correlations, which are not supported by standard statistical processors.
%%
In this work, we focus on a similar approach to deriving insight and even new hypotheses through the data rather than using it just for confirmatory analysis.
%An alternative data-driven approach is described as follows.
%%
% \paragraph{Data Driven Hypothesis-Generation-based Analysis.}
% We already described an Interactive Visual Analysis approach for image-centric cohort study data, which connects to the variable listing step \cite{Klemm2014VIS}.
% %%
% The methods aim to derive hypotheses through analysis of the data and observations about previously unknown feature correlations.
% %%
% Employing \emph{hypotheses generation} requires overview visualizations of feature correlations, which are not supported by standard statistical processors.

\subsection{Epidemiological Data} \label{sec:EpidemiologicalData}
%%
%\com{Bernhard: Due to overlaps to VIS'14 paper in this section, this can be shortened. E.g. "More discussion of data types and characteristics can be found in [...]"}
%%
There are many data acquisition modalities available to epidemiologists, which are suitable for different analysis types.
%%
%We focus on cohort studies are a major epidemiological tool for gathering epidemiological features.
We focus on cohort studies, which impose the largest data sets and yield a highly heterogenous and incomplete information space.
%%
Subject data are collected either towards a specific disease or with the widest range possible.
%%
The latter allows the data set to be assessed towards different diseases.
%%
The feature space comprises information about lifestyle, somatometric variables, medical parameters, genetic data as well as medical images.
%%
These features are derived through different modalities, such as questionnaires, medical examinations or laboratory analyses.
%%
Many features are sparse, such as follow up questions about a medication or treatment of a certain disease.
%%
Other features are exclusive for a sub-group, such as women-specific questions, e.g., number of born children or period status.
%%
%\com{Restriction of amount of data because it must not be triangulated and because the ethics committees are very restrictive}
%%
%\paragraph{Data Types.}
%%
Medical status features or lifestyle factors are often of \emph{dichotomous} (binary) type.
%%
%The data space comprises continuous variables (somatometric variables, such as body weight) as well as categorical variables (e.g. graduation type).
%%
%The data heterogeneity has to be taken into account when the analysis method is chosen.
%%
Continuous data are often discretized (e.g. 10 year steps for age) to equalize the variable types and to simplify the method selection.
%%
However, this should be avoided, since it reduces the information space and also introduces a new information bias, as assumptions are modeled through the discretization.
%%

Medical image data is also acquired and analyzed in modern cohort studies.
%%
We incorporate image-derived features, but do not put focus on analyzing image data.
%%
More discussion of cohort study data types and characteristics can be found in \cite{Klemm2014VIS, Toennies2015, Preim2014}.
%%
%\paragraph{Image Data.}
% \com{Can probably be cut (reference to Klaus' Paper for more details on this) (see Bernhards comment above)}
% %%
% Since the Rotterdam study, many modern cohort studies include medical image data.
% %%
% For ethical reasons, the imaging modalities usually not include ionizing radiation.
% %%
% The image quality is often inferior to clinical standards, which is a tradeoff between time and cost \cite{Preim2014}.
% %%
% These data are hard to analyze as they require segmentations to outline structures of interest.
% %%
% This process is prone to inter- and intra-observer variability when carried out manually.
% %%
% Automatic or semi-automatic solutions are a remedy for this problem, but are costly and need to be tailored to the structure of interest \cite{Toennies2015}.
% %%
% Image-derived variables are either dichotomous variables indicating a medical finding by a radiologist or continuous, describing the shape of segmented structures (e.g. volume or diameter).
\\\\
%\paragraph{Confounding Features.}
Features influencing the exposure as well as the outcome of an analysis are called \emph{confounders} and have to be specially treated.
%Confounding features have to be considered in epidemiological analysis, as they influence both the exposure as well as the outcome of an analysis.
%%
%Features influencing the exposure as well as the outcome of an analysis are called confounders.
%%
The analysis model has to be adjusted by normalizing all included features towards the confounder.
%%
\emph{Age} is included as confounder in almost any epidemiological analysis, since most diseases (such as different cancer types) are more likely with increasing age.
%%
It also influences the general body condition and thereby almost all features acquired through cohort studies.
%%
Another important confounder is \emph{gender}.
%%
Other confounders have to be selected by epidemiologists specific to the investigated condition.

@@

\paragraph{Regression Analysis Notation.} Regression formulas are usually denoted as follows:
%%
\begin{equation}
Dependent \sim Independent_1 + ... + Independent_n
%Dependent \sim \sum_{i=1}^n Independent_i
\label{eq:RegressionNotation}
\end{equation}
%%
A example of a regression formula would be $KidneyDisorder \sim Smoking + Obesity$.
The most used regression operators comprise:
%%
\begin{itemize}
	\item $+,-$ inclusion/exclusion of the variable,
	\item $:$ inclusion of interactions between the variables (e.g. $x:y$),
	\item $*$ inclusion the variables as well as their interactions (e.g. $x*y$)
	\item $|$ (conditioning) inclusion of variable x, given y (e.g. $x|y$)
\end{itemize}
%%
The type of the target feature restricts the regression type.
%%
Different regression types are available, we focus on the following:
%%
\paragraph{Linear Regression for Continuous Target.} The basic type is the linear regression, creating a linear map from the space comprising the \emph{independent} features to the \emph{dependent} features.
%%
The \emph{dependent} variable has to be of a continuous type.
%%

\paragraph{Logistic Regression for Dichotomous Target.} Logistic regression implies a dichotomous target variable.
%%
The target is described by fitting a logistic function.
%%
Logistic models as opposed to linear models do not allow for extracting an $R^2$ quality of fit value.
%%
Therefore, pseudo-$R^2$ values are extracted, such as the \emph{Nagelkerke $R^2$}, which mimics the behavior of the $R^2$.
%%
\emph{Nagelkerke $R^2$} behave different than $R^2$ values extracted from linear regression model.
%%
Comparisons have to be handled with care.

@@

\subsection{The Study of Health in Pomerania (SHIP)}
The \texttt{SHIP}, located in Northern Germany, aims to characterize health and disease in the widest range possible \cite{Volzke2011}.
%%
It does not focus on a specific disease, making the data set open for many diseases.
%%
Unique for the \texttt{SHIP} is the acquisition of medical image data per cohort subject.
%%
A second cohort, \texttt{SHIP-TREND} was started in 2012.
%%
Data for both cohorts are examined in a 5-year time span.
%%
New parameters are added in each iteration, extending the range of investigated diseases.
%%
For the latest two acquisitions (\texttt{SHIP-2} and \texttt{SHIP-TREND-0}), MRI scans are included into the cohort \cite{Hegenscheid2009, Ivanovska2014}.
%%
However, most examinations occur in all stages and are performed according to the same instructions to enable comparisons over the different stages of the study. % ("\emph{method loyality}").
%%
%Starting in 1997 with a cohort of 4,308 subjects, the \texttt{SHIP}, located in Northern Germany, aims to characterize health and disease in the widest range possible \cite{Volzke2011}.
%After the pioneering Rotterdam study (started in 1990), several MR imaging study initiatives were initiated.
%
%They slightly differ in clinical focus, acquired data and epidemiological research questions.
%
%Starting in 1997 with a cohort of 4,308 subjects, the \texttt{SHIP}, located in Northern Germany, aims to characterize health and disease in the widest range possible \cite{Volzke2011}.
%
%Data are collected without focus on a group of diseases.
%
%This allows to query the data regarding many diseases and conditions.
%
%
\section{Prior and Related Work}
%% https://en.wikipedia.org/wiki/Exploratory_data_analysis#cite_note-Tukey1977-4
In 1977, Tukey already stated that data is too often only analyzed using confirmatory data analysis \cite{Tukey}.
%%
He emphasized the need to use data to derive hypotheses instead, which can then be tested again.
%%
In this section we present prior and related work trying to achieve this goal.
%%
%We put each paper in relation to our work, derive ideas and point out differences, starting with the works closest to ours:
%%
\\\\
The work of Piringer et al. \cite{Piringer}, Chan et al. \cite{Chan}, Angelelli et al. \cite{Angelelli} and Zhang et al. \cite{Zhang2014} are closest related to ours regarding different aspects.
%% HyperMoVal: Interactive Visual Validation of Regression Models for Real-Time Simulation
Akin to our approach, Piringer et al. \cite{Piringer} propose methods for visualizing regression analysis results and properties for developing car engines.
%%
Their main goal is to assess the pairwise influence of independent features towards the target feature using a plot matrix displaying models as contours.
%%
They also incorporate 3D visualizations for each pairwise combination, but mainly because its popularity with their target domain engineers.
%%
Linked views of model deviations allow to select outliers.
%%
This limits the method to comparing a few models at once as the plot matrix gets complex with increasing feature number.
%%
The main difference is their focus on analyzing one complex model in detail, yielding extensive plots, while we analyze a large amount of simpler models towards \emph{different} features.
%%
They also focus on metric features, while we process categorical data as well.
%%
%We share the matrix-arrangement of results depicting relationships between independent features in a model.

@@

%% TODO: Check DLPD for correct page numbers
While the presented techniques were well received by the epidemiological experts, the explanatory power towards back pain was limited, yielding an analysis based on image-derived features, such as extracting and analyzing curvature, torsion and angle of the lumbar spine \cite{Klemm2015}.
%%
%These measures were analyzed using a novel decision tree quality plot towards non-image data.
%%
We concluded that the model quality is insufficient to characterize back pain.
\\\\
The difference of the presented approach towards our previous and related work is twofold:
\begin{enumerate}
	\item We focus on large scale analysis of a vast number of linear and logistic regression-models by assessing their quality-of-fit using descriptive metrics.
	\item The analysis is conducted towards a target feature and incorporates expert knowledge via the regression model definition rather than subdividing the underlying data.
\end{enumerate}
%%
\section{Regression Cube Analysis of Cohort Study Data}
% TODO: Do we need a preprocessing section?
%\com{Add Data Preprocessing Section.}
%%
The basic idea of our \emph{Regression Cube} is to provide an overview visualization of large cohort study data sets towards target features.
%%
Overview visualizations of feature relationships as presented by Angelelli et al. \cite{Angelelli} are often focused on relationships between the visualized features.
%%
Correlation metrics, such as the \emph{Pearson product-moment correlation coefficient} or \emph{Cram\'{e}r's V} contingency values are incorporated to achieve this goal.
%%
In epidemiology, these relationships are also of interest, but rather w.r.t. their explanatory power towards the target feature.
%%
These target features often indicate the presence of the investigated disease.
%%
As described in Section \ref{sec:RegressionAnalysis}, regression analysis is the statistical tool of choice for analyzing these relationships.
%%
% unified -> singular [Steffi?]
A regression model is based on expert knowledge, there is no singular rule how to apply them to a given set of features. Thus, they have to be applied with care.
%%
\subsection{Cube Description Using Regression Formula Notation}
%%
Expert knowledge is integrated into regression analysis by the regression formulas.
%%
As described in Section~\ref{sec:RegressionAnalysis}, the formula input influences the type of the chosen regression method as well as the \emph{independent} features describing the target.
%%
%In order to calculate all combinations of two to three independent features, we can apply  \emph{Regression Cube} aims to 
%%

@@

The major advantage of this notation is that it comes natural to anyone familiar with regression analysis since it is the standard way of expression.
